\fancyhead[RE,LO]{\footnotesize{LIST OF PUBLICATIONS} \hspace{0.5em} {\footnotesize\rightmark} }
\renewcommand{\headrulewidth}{0.5pt}
%
\chapter{List of Publications}
\begin{center}
\textbf{\Large \underline {International Journal Papers}} \\
\end{center}
\begin{enumerate}
%
%\item \textbf{Sajal Halder} and Young-Koo Lee. \textit{Supergrpah based Periodic Behaviors Mining in Dynamic Networks}. In submission.

\item  \textbf{Sajal Halder}, Yongkoo Han, A. M. Jehad Sarkar and Young-Koo Lee. \textit{An Entertainment Recommendation System using the Dynamics of User Behavior over Time}. Decision in process in the Journal of Systems and Software.

\item	Md. Rezaul Karim, \textbf{Sajal Halder} , Byeong-Soo Jeong, and Ho-Jin Choi. \textit{Efficient Mining Frequently Correlated, Associated-correlated and Independent Patterns Synchronously by Removing Null Transactions}. Human Centric Technology and Service in Smart Space, pages 93-103, 2012. 

%\vspace{0.1in}
\item \textbf{Sajal Halder}, A. M. Jehad Sarkar and Young-Koo Lee. \textit{A synthetic trajectory-based moving objects generator}. Under review  in International Journal of Artificial Intelligence Tools.

\item \textbf{Sajal Halder}, Md. Mostofa Kamal Rasel, Yongkoo Han, and Young-Koo Lee. \textit{Mining Spatiotemporal Moving Objects Swarm}. Under review in Kyung Hee University Journal..

\pagebreak


%
\begin{center}
\textbf{\Large \underline{International Conference Papers}} 
\end{center}

\item Sajal Halder, Yongkoo Han and Young-Koo Lee. \textit{Discovering Periodic Patterns using Supergraph in Dynamic Networks}. Accepted in 5th International Conference on Data Mining and Intelligent Information Technology Applications (ICMIA),Jun 18-20, South Korea, 2013.

%
\item Sajal Halder, A. M. Jehad Sarkar and Young-Koo Lee. \textit{Movie Recommendation System Based on Movie Swarm}. Second International Conference on Cloud and Green Computing (CGC), China, Nov 1-3, 2012.
%\vspace{0.1in} 
\item Sajal Halder, Md. Samiullah, A. M. Jehad Sarkar and Young-Koo Lee. \textit{MovieSwarm: Information Mining technique for Movie Recommendation System}. In the 7th International Conference on Electrical and Computer Engineering (ICECE), Bangladesh, Dec 20-22, 2012.


\begin{center}
\textbf{\Large \underline{Thesis/Project Works}} 
\end{center}

\item Sajal Halder, Uzzal Kumar Dutta, Uttam Kumer Biswas and Asish Kumar Biswas ``Classification of Multiple Protein Sequences by means of Irredundant Patterns'', B.Sc. Final Year Project, Department of Computer Science and Engineering (CSE), University of Dhaka (DU), Bangladesh, February, 2011.
%
%\item Sabbir Ahmed, Md. Obaidur Rahman, Saifur Rahman Pir, M. A. Mottalib and Md. Saiful Islam; \textquotedblleft A New Approach towards the Development of English to Bangla Machine Translation System\textquotedblright, \textit{B.Sc. Engg. Final Year Project, Department of Computer Science $\&$ Information Technology (CIT), Islamic University of Technology (IUT)}, Bangladesh, September, 2003
%
\end{enumerate}
%
